Summary Tables

### 2023-08-24 summary_tables.Rmd
updated comments

# WARNING: This script only works if ITHIM-Global has been run in constant mode!

@@

```{r message=F, error=F, warning=FALSE}
# call get_scen_settings function to find the mode split for each distance category for each city
get_scen_settings <- ithimr::get_scenario_settings(cities)

>>>>

# WARNING: This script only works if ITHIM-Global has been run in constant mode using either the BOGOTA, LATAM, AFRICA_INDIA or GLOBAL scenario definitions

@@

```{r message=F, error=F, warning=FALSE}
# call get_scen_settings function to find the mode split for each distance category for each city

get_scen_settings <- ithimr::get_scenario_settings(cities = cities)
